---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CureDepCens

<!-- badges: start -->
<!-- badges: end -->

Cure dependent censoring regression models for long-term survival multivariate data.

## Installation

You can install the development version of CureDepCens from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("GabrielGrandemagne/CureDepCens")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(devtools)
library(CureDepCens)
load_all()
Dogs_MimicData <- Dogs_MimicData
delta_t = ifelse(Dogs_MimicData$cens==1,1,0)
delta_c = ifelse(Dogs_MimicData$cens==2,1,0)

# MEP
fit <- cure_dep_censoring(formula = time ~ x1_cure + x2_cure | x_c1 + x_c2,
                           data = Dogs_MimicData,
                           delta_t = delta_t,
                           delta_c = delta_c,
                           ident = Dogs_MimicData$ident,
                           dist = "mep")
summary_cure(fit)
```

*Dogs_MimicData* is our simulated data frame. For more information check the documentation for stored datasets.

```{r}
head(Dogs_MimicData)
```

You can also plot the survival function

```{r plot_cure}
plot_cure(fit, scenario = "t")
```
