---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CureDepCens

<!-- badges: start -->
<!-- badges: end -->

Dependent censoring regression models with cure fraction for survival multivariate data.

## Installation

You can install the development version of CureDepCens from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("GabrielGrandemagne/CureDepCens")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#install.packages("devtools")
#devtools::install_github('GabrielGrandemagne/CureDepCens')
library(CureDepCens)

fit_mep <- cure_dep_censoring(formula = time ~ x1_cure + x_c2 | x_c1 + x_c2,
                           data = simula_fracur,
                           delta_t = simula_fracur$delta_t,
                           delta_c = simula_fracur$delta_c,
                           ident = simula_fracur$ident,
                           dist = "mep")
summary_cure(fit_mep)
```

*simula_fracur* is our simulated data frame. For more information check the documentation for stored datasets.

```{r}
head(simula_fracur)
```

You can also plot the survival function

```{r plot_cure}
plot_cure(fit_mep, scenario = "t")
```
